### 2019-02-07 2-Chapters/1-Chapter/chapter1.tex
Starting to fill the sections of each chapters, to have an overview of the organization
Fix #4

% First chapter begins here
\chapter{Continuous Phase Modulation for Aeronautical Telemetry }
\label{chapter:1}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/1-Chapter/Images/}}
\section{CPM signal model}
\label{sec:CPM_signal_model}

>>>>

% First chapter begins here
\chapter{Introduction}
\label{chapter:1}
\minitoc
\newpage
% Write miniTOC just after the title
\graphicspath{{2-Chapters/1-Chapter/Images/}}

% ----------------------------------------------------------------------------
\section{Considered problems}
\label{sec:1:problems}

% ----------------------------------------------------------------------------
\section{Considered solutions}
\label{sec:1:solutions}

% ----------------------------------------------------------------------------
\section{Overview of the contributions}
\label{sec:1:contributions}

% ----------------------------------------------------------------------------
\section{List of publications}
\label{sec:1:contributions}

% =============================================================================
\subsection{Publications in international conferences with proceedings}

\begin{itemize}
\item
    \emph{GNU Radio Implementation of MALIN: ``Multi-Armed bandits Learning for Internet-of-things Networks''},
    by \textbf{Lilian Besson}, Rémi Bonnefoi \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2019.ieee-wcnc.org}), Marrakech, Morocco, April 2019,
    \texttt{hal.inria.fr/hal-02006825}.

\item
    \emph{Multi-Player Bandits Revisited}},
    by \textbf{Lilian Besson} \& Emilie Kaufmann.
    \emph{Algorithmic Learning Theory} (ALT, \texttt{www.cs.cornell.edu/conferences/alt2018}), Lanzarote, Spain, April 2018,
    \texttt{hal.inria.fr/hal-01629733}.

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access}},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \texttt{wcnc2018.ieee-wcnc.org}), Barcelone, Spain, April 2018,
    \texttt{hal.inria.fr/hal-01705292}.

\item
    \emph{Multi-Armed Bandit Learning in IoT Networks and non-stationary settings}},
    by Rémi Bonnefoi, \textbf{Lilian Besson}, Christophe Moy, Emilie Kaufmann \& J. Palicot.
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} (CROWNCOM, \texttt{crowncom.org/2017}), Lisboa, Portugal, Septembre $2017$,
    \texttt{hal.inria.fr/hal-01575419},
    \textbf{Best Paper Award}.

\end{itemize}

% =============================================================================
\subection{Submitted works or in progress works waiting for a new submission}

\begin{itemize}
\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits}},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, February $2019$,
    \texttt{hal.inria.fr/hal-02006471}.

\item
    \emph{Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions},\\
    by Rémi Bonnefoi, \textbf{Lilian Besson}, J. Manco-Vasquez \& Christophe Moy.
    Submitted for MOTIoN workshop (\texttt{sites.google.com/view/wcncworkshop-motion2019}), February $2019$.

\item
    \emph{SMPyBandits: an Open-Source Research Framework for Single and Multi-Players Multi-Arms Bandits (MAB) Algorithms in Python},
    by \textbf{Lilian Besson}, active development since October $2016$,
    \texttt{hal.inria.fr/hal-01840022}.
    About $40000$ lines of code, hosted on \texttt{GitHub.com/SMPyBandits},
    with a complete documentation on \texttt{SMPyBandits.rtfd.io}.

\item
    \emph{What Doubling-Trick Can and Can't Do for Multi-Armed Bandits},\\
    by \textbf{Lilian Besson} \& Emilie Kaufmann, September $2018$,
    \texttt{hal.inria.fr/hal-01736357}.

\item
    \emph{MALIN: ``Multi-Arm bandit Learning for Iot Networks'' with GRC: A TestBed Implementation and Demonstration that Learning Helps},
    by \textbf{Lilian Besson}, Rémi Bonnefoi, Christophe Moy.
    Demonstration presented at \emph{International Conference on Communication} (ICT, \texttt{ict-2018.org/demos}), in Saint-Malo, France in June $2018$.
    See \texttt{YouTu.be/HospLNQhcMk} for a $6$-minutes presentation video.

\item
    \emph{A Note on the Ei Function and a Useful Sum-Inequality},
    by \textbf{Lilian Besson},
    February $2018$,
    \texttt{hal.inria.fr/hal-01847480}.

\end{itemize}

% =============================================================================
\subsection{Presentations in seminars and conferences}

\paragraph{Seminars} I gave some presentations in the following events:
    SequeL team seminar at Inria Lille in September and December $2017$, and June $2019$;
    SCEE team seminar at CentraleSupélec, Rennes campus, in October $2017$, February $2018$ and June $2019$;
    as well as
    for the GDR ISIS day held in Issy-les-Moulineaux on November $2017$,
    for the brown-bag seminar at ENSAI in Bruz in January $2018$,
    for the weekly CMAP seminar at École Polytechnique in October $2018$.

\paragraph{Tutorial}
    I gave a tutorial\footnote{Cf. \texttt{hal.archives-ouvertes.fr/cel-01830248}} on the Julia language, at IETR seminar in Vannes in June $2018$,
    with Pierre Haessig (\texttt{pierreh.eu}).

\paragraph{Training}
    I was also in charge of ``GouTP'' training sessions for about $30$ PhD students at CentraleSupélec Rennes.
    We had a lot of various $1$h training sessions between January $2017$ and June $2019$,
    and I gave about $10$ training, on various topics including Python, \texttt{git}, HAL and arXiv, the Julia language and Bib\TeX{}.

% =============================================================================
\subsection{Other experiences}

\paragraph{Conferences} I attended the following conferences:
	\emph{International Conference on Communication} ICC (Paris), May $2017$,
    \emph{Conference on Learning Theory} COLT (Amsterdam), July $2017$,
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} CROWNCOM (Lisboa), September $2017$,
    \emph{Conference on Algorithmic Learning Theory} ALT (Lanzarote), April $2018$,
    \emph{Wireless Communication and Networking Conference} WCNC (Barcelona), April $2018$,
	\emph{International Conference on Telecommunication} ICT (Saint-Malo), June $2018$,
    \emph{Wireless Communication and Networking Conference} WCNC (Marrakech), April $2019$,
    \emph{Colloque francophone de traitement du signal et des images} GRETSI (Lille), August $2019$.

\paragraph{Seminars} I attended the following seminars:
	\emph{Workshop Learn with Earning} (Rotterdam), May $2018$,
	\emph{Workshop on Optimization and Learning} (Toulouse), September $2018$,
	\emph{European Workshop on Reinforcement Learning} (Lille), October $2018$,

\paragraph{Responsabilities}
    president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{Cf. \texttt{bitbucket.org/scee_ietr/phd-student-day-ietr-2017-bonnefoi-and-besson/downloads/poster.pdf}}.
    I also helped for the organization and presented another poster\footnote{Cf. \texttt{bitbucket.org/lbesson/phd-student-day-ietr-2018/downloads/poster.pdf}} at IETR seminar (\texttt{seminar-ietr-18.sciencesconf.org}), held in Vannes in June $2018$.

    \paragraph{Reviews}
	for \emph{European Workshop on Reinforcement Learning} (Lille) \texttt{ewrl.wordpress.com/ewrl14-2018}, in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \uref{https://nips.cc/Conferences/2018/}{\emph{NeurIPS}} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.

\paragraph{System Administrator}
	maintaining our workstations running GNU/Linux and Windows
	at SCEE team,
	and our cognitive radio test-bed using USRP cards and the GNU Radio software,
	from January $2017$ to June $2019$.

### 2019-02-07 4-Listofpublications/Listofpublications.tex
Fix #4

% \section*{International Journals}
% \renewcommand{\labelenumi}{[IJ-\arabic{enumi}]}
% \begin{etaremune}%[label={[RI-\arabic*]}]
% 	\item \textbf{L. Besson}, Skrzypczak, A., E. Kaufmann `` Reduced Complexity Detectors Based on SOQPSK Linearzations,'', in \emph{IEEE Transactions on Aerospace and Electronic Systems}, 2018 (Major Revision)
% 	\item \textbf{L. Besson}, Skrzypczak, A., E. Kaufmann, `` PAM Decomposition of Ternary CPM With Duobinary Encoding,'', in \emph{IEEE Transactions on Communications}, vol. 65, no. 10, pp. 4274-4284, doi: 10.1109/TCOMM.2017.2723567, Oct 2017
% \end{etaremune}

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
	% \item \textbf{L. Besson}, E. Kaufmann, Skrzypczak, A. ``Linear Decision Feedback Detector for SOQPSK,'', in \emph{URSI AP-RASC}, 2019 (Submitted)
\item
  \href{https://perso.crans.org/besson/articles/BBM__IEEE_WCNC_2019.pdf}{GNU
  Radio Implementation of MALIN: « Multi-Arm bandits Learning for
  Internet-of-things Networks »}, par \textbf{L. Besson},
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, avril 2019.
\item
  \href{https://perso.crans.org/besson/articles/BBM__Demo_ICT_2018.pdf}{MALIN:
  « Multi-Arm bandit Learning for Iot Networks » with GRC: A TestBed
  Implementation and Demonstration that Learning Helps}, par \textbf{L.
  Besson}, \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}. Démonstration
  présentée à ICT (\emph{International Conference on Communication}),
  Saint-Malo, France, juin 2018. Cf. \texttt{YouTu.be/HospLNQhcMk}
\item
  \href{https://hal.inria.fr/hal-01629733/document}{Multi-Player Bandits
  Revisited}, par \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  \href{http://www.cs.cornell.edu/conferences/alt2018/accepted.html}{ALT}
  (\emph{Algorithmic Learning Theory}), Lanzarote, Espagne, avril 2018,
  \href{https://hal.inria.fr/hal-01629733}{HAL-01629733}.
\item
  \href{https://hal.inria.fr/hal-01705292/document}{Aggregation of
  Multi-Armed Bandits learning algorithms for Opportunistic Spectrum
  Access}, par \textbf{L. Besson},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2018.ieee-wcnc.org/}{IEEE WCNC}, Barcelone, Espagne,
  avril 2018, \href{https://hal.inria.fr/hal-01705292}{HAL-01705292}.
\item
  \href{https://hal.inria.fr/hal-01575419/document}{Multi-Armed Bandit
  Learning in IoT Networks and non-stationary settings}, par
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L.
  Besson}, \href{https://moychris.wordpress.com/}{C. Moy},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& J. Palicot. \href{http://crowncom.org/2017/}{CrownCom}
  (\emph{Conference on Cognitive Radio Oriented Wireless Networks}),
  Lisbonne, Portugal, septembre 2017,
  \href{https://hal.inria.fr/hal-01575419}{HAL-01575419}, \textbf{prix
  du meilleur article}.
\end{etaremune}

@@

\section*{Other Publications}
\renewcommand{\labelenumi}{[OP-\arabic{enumi}]}
\begin{etaremune}
\item
	\href{https://perso.crans.org/besson/articles/BMBBM__IEEE_WCNC__2019.pdf}{Upper-Confidence
	Bound for Channel Selection in LPWA Networks with Retransmissions},
	par \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, J.
	Manco-Vasquez, \textbf{L. Besson},
	\href{https://cfaouzi-bader.com/}{F. Bader},
	\href{https://moychris.wordpress.com/}{C. Moy}. Septembre 2018.
\item
	\href{https://hal.inria.fr/hal-01840022/document}{SMPyBandits: an
	Open-Source Research Framework for Single and Multi-Players Multi-Arms
	Bandits (MAB) Algorithms in Python}, par \textbf{L. Besson},
	développement depuis octobre 2016 et encore actif,
	\href{https://hal.inria.fr/hal-01840022}{HAL-01840022}. Code sur
	\href{https://GitHub.com/SMPyBandits/SMPyBandits}{GitHub.com/SMPyBandits}
	(environ 40000 lignes), documentation sur
	\href{https://SMPyBandits.rtfd.io}{SMPyBandits.rtfd.io}.
\item
	\href{https://hal.inria.fr/hal-01736357/document}{What Doubling-Trick
	Can and Can't Do for Multi-Armed Bandits}, par \textbf{L. Besson} \&
	\href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
	Kaufmann}, septembre 2018,
	\href{https://hal.inria.fr/hal-01736357}{HAL-01736357}.
\item
	\href{https://hal.inria.fr/hal-01847480/document}{A Note on the Ei
	Function and a Useful Sum-Inequality}, par \textbf{L. Besson}, février
	2018 \href{https://hal.inria.fr/hal-01847480}{HAL-01847480}.
\end{etaremune}

% \section*{Patents}
% \renewcommand{\labelenumi}{[PT-\arabic{enumi}]}
% \begin{etaremune}
% \item \textbf{L. Besson}, E. Kaufmann, Skrzypczak, A. `` Nouvelle architecture de d\'{e}codage spatio-temporel bas\'{e}e sur la d\'{e}composition PAM pour la modulation SOQPSK-TG,'' (pending)
% \end{etaremune}

>>>>

% \section*{International Journals}
% \renewcommand{\labelenumi}{[IJ-\arabic{enumi}]}
% \begin{etaremune}%[label={[RI-\arabic*]}]
% 	\item \textbf{L. Besson}, E. Kaufmann ``XXX'',, in \emph{XXXX}, 2018 (Major Revision)
% \end{etaremune}

\section*{International Conferences}
\renewcommand{\labelenumi}{[IC-\arabic{enumi}]}
\begin{etaremune}
\item
  \href{https://perso.crans.org/besson/articles/BBM__IEEE_WCNC_2019.pdf}{GNU
  Radio Implementation of MALIN: « Multi-Armed bandits Learning for
  Internet-of-things Networks »}, par \textbf{L. Besson},
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2019.ieee-wcnc.org/}{IEEE WCNC},
  Marrakech, Maroc, avril 2019.
\item
  \href{https://perso.crans.org/besson/articles/BBM__Demo_ICT_2018.pdf}{MALIN:
  « Multi-Arm bandit Learning for Iot Networks » with GRC: A TestBed
  Implementation and Demonstration that Learning Helps}, par \textbf{L.
  Besson}, \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi},
  \href{https://moychris.wordpress.com/}{C. Moy}. Démonstration
  présentée à ICT (\emph{International Conference on Communication}),
  Saint-Malo, France, juin 2018. Cf. \texttt{YouTu.be/HospLNQhcMk}
\item
  \href{https://hal.inria.fr/hal-01629733/document}{Multi-Player Bandits
  Revisited}, par \textbf{L. Besson} \&
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann}.
  \href{http://www.cs.cornell.edu/conferences/alt2018/accepted.html}{ALT}
  (\emph{Algorithmic Learning Theory}), Lanzarote, Espagne, avril 2018,
  \href{https://hal.inria.fr/hal-01629733}{HAL-01629733}.
\item
  \href{https://hal.inria.fr/hal-01705292/document}{Aggregation of
  Multi-Armed Bandits learning algorithms for Opportunistic Spectrum
  Access}, par \textbf{L. Besson},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& \href{https://moychris.wordpress.com/}{C. Moy}.
  \href{http://wcnc2018.ieee-wcnc.org/}{IEEE WCNC}, Barcelone, Espagne,
  avril 2018, \href{https://hal.inria.fr/hal-01705292}{HAL-01705292}.
\item
  \href{https://hal.inria.fr/hal-01575419/document}{Multi-Armed Bandit
  Learning in IoT Networks and non-stationary settings}, par
  \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L.
  Besson}, \href{https://moychris.wordpress.com/}{C. Moy},
  \href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
  Kaufmann} \& J. Palicot. \href{http://crowncom.org/2017/}{CrownCom}
  (\emph{Conference on Cognitive Radio Oriented Wireless Networks}),
  Lisbonne, Portugal, septembre 2017,
  \href{https://hal.inria.fr/hal-01575419}{HAL-01575419}, \textbf{prix
  du meilleur article}.
\end{etaremune}

@@

\section*{Other Publications}
\renewcommand{\labelenumi}{[OP-\arabic{enumi}]}
\begin{etaremune}
\item
	\href{https://perso.crans.org/besson/articles/BMBBM__IEEE_WCNC__2019.pdf}{Upper-Confidence
	Bound for Channel Selection in LPWA Networks with Retransmissions},
	par \href{https://remibonnefoi.wordpress.com/}{R. Bonnefoi}, \textbf{L. Besson}, J.
	Manco-Vasquez,
	\href{https://moychris.wordpress.com/}{C. Moy}. Septembre 2018.
\item
	\href{https://hal.inria.fr/hal-01840022/document}{SMPyBandits: an
	Open-Source Research Framework for Single and Multi-Players Multi-Arms
	Bandits (MAB) Algorithms in Python}, par \textbf{L. Besson},
	développement depuis octobre 2016 et encore actif,
	\href{https://hal.inria.fr/hal-01840022}{HAL-01840022}. Code sur
	\href{https://GitHub.com/SMPyBandits/SMPyBandits}{GitHub.com/SMPyBandits}
	(environ 40000 lignes), documentation sur
	\href{https://SMPyBandits.rtfd.io}{SMPyBandits.rtfd.io}.
\item
	\href{https://hal.inria.fr/hal-01736357/document}{What Doubling-Trick
	Can and Can't Do for Multi-Armed Bandits}, par \textbf{L. Besson} \&
	\href{http://chercheurs.lille.inria.fr/ekaufman/research.html}{E.
	Kaufmann}, septembre 2018,
	\href{https://hal.inria.fr/hal-01736357}{HAL-01736357}.
\item
	\href{https://hal.inria.fr/hal-01847480/document}{A Note on the Ei
	Function and a Useful Sum-Inequality}, par \textbf{L. Besson}, février
	2018 \href{https://hal.inria.fr/hal-01847480}{HAL-01847480}.
\end{etaremune}

% \section*{Patents}
% \renewcommand{\labelenumi}{[PT-\arabic{enumi}]}
% \begin{etaremune}
% \item \textbf{L. Besson}, E. Kaufmann. ``XXX'', (pending)
% \end{etaremune}
